---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load_preprocess}
data <- read.csv('data/activity.csv')
```


## What is mean total number of steps taken per day?
```{r steps_per_day}
daily <- aggregate(data$steps, by=list(data$date), FUN=sum)
meanSteps <- mean(daily$x, na.rm=TRUE)
medianSteps <- median(daily$x, na.rm=TRUE)
hist(daily$x, breaks=10, col="blue", xlab="Steps per day", main="Steps per day")
```


On average, a person did `r sprintf("%.2f",meanSteps)` steps per day, with median value being `r medianSteps`.


## What is the average daily activity pattern?

```{r daily_activity}
avgInt <- aggregate(steps ~ interval, data, mean )
maxAvg <- avgInt[avgInt$steps==max(avgInt$steps),]
plot(avgInt$interval, avgInt$steps,type="l",
     main="Average number of steps per time interval", 
     xlab="Interval", ylab="Steps")
```

On average, the most steps (`r sprintf("%.2f",maxAvg$steps)`) were done in the interval number `r maxAvg$interval`

## Imputing missing values

The dataset has `r nrow(data[is.na(data$steps),])` rows with missing values for number of steps. To fix it, the missing values will be replaced with the average values for the corresponding time interval.

```{r missing_data2}
dataFixed <- merge(data, avgInt, by=c("interval"))
names(dataFixed) = c('interval', 'steps', 'date', 'avgSteps')
dataFixed$avgSteps <- round(dataFixed$avgSteps)
dataFixed$steps[is.na(dataFixed$steps)] <- dataFixed$avgSteps[is.na(dataFixed$steps)]
dataFixed$avgSteps <- NULL
daily <- aggregate(dataFixed$steps, by=list(dataFixed$date), FUN=sum)
meanSteps <- mean(daily$x)
medianSteps <- median(daily$x)
hist(daily$x, breaks=10, col="blue",
     xlab="Steps per day", 
     main="Steps per day (missing values fixed)")

```

On average, a person did `r sprintf("%.2f",meanSteps)` steps per day, with median value being `r sprintf("%.2f",medianSteps)`. As we can see, imputing missing values only slightly affected those values.

## Are there differences in activity patterns between weekdays and weekends?
``` {r weekdays}
library(ggplot2)
dataFixed$date <- as.Date(dataFixed$date)
dataFixed$weekday <- weekdays(dataFixed$date)
dataFixed$weekend <- "weekday"
dataFixed[dataFixed$weekday %in% c("Saturday","Sunday"),"weekend"] <- "weekend"
dataFixed$weekend <- factor(dataFixed$weekend)
avgDays <-aggregate(dataFixed$steps, 
                    list(interval=dataFixed$interval, 
                         weekend = dataFixed$weekend), mean)
g <- ggplot(avgDays, aes(interval, x))
g <- g + geom_line(stat="identity")
g <- g+labs( x="interval", y="steps")
g <- g+ ggtitle("Steps on weekdays and weekends")
g <- g  + facet_grid(weekend ~.)
print(g) 
```
