---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load_preprocess}
data <- read.csv('data/activity.csv')
```


## What is mean total number of steps taken per day?
```{r steps_per_day}
daily <- aggregate(data$steps, by=list(data$date), FUN=sum)
meanSteps <- mean(daily$x, na.rm=TRUE)
medianSteps <- median(daily$x, na.rm=TRUE)
hist(daily$x, xlab="Steps per day", main="Steps per day")
```


On average, a person did `r sprintf("%.2f",meanSteps)` steps per day, with median value being `r medianSteps`.


## What is the average daily activity pattern?

```{r daily_activity}
avgInt <- aggregate(steps ~ interval, data, mean )
maxAvg <- avgInt[avgInt$steps==max(avgInt$steps),]
plot(avgInt$interval, avgInt$steps,type="l", main="Average number of steps per time interval", xlab="Interval", ylab="Steps")
```

On average, the most steps (`r sprintf("%.2f",maxAvg$steps)`) were done in the interval number `r maxAvg$interval`

## Imputing missing values

```{r missing_data}

```


## Are there differences in activity patterns between weekdays and weekends?
